Rotations and Insecticide Resistance initial plots

### 2017-11-22 inst/documents/rotations_notes.Rmd
move checking and switching of insecticides into 2 functions

*22/11/17*

@@

@@

>>>>

*22/11/17*
~ added sentence about interval 0 RwR to the UI

~ removed this commented out alternative to df_results
  #experimental
  # df_res_active <- data.frame(generation=rep(1:max_gen,n_insecticides),
  #                       insecticide=NA,
  #                       region=NA,
  #                       resistance=NA, stringsAsFactors = FALSE)
  # df_res_refuge <- df_res_active

~ I can redesign the insecticide switch function slightly :

to pass :
current_insecticide
n_insecticides
RAF1gen
df_results : to allow assessment of which insecticides have been used previously

return :
current_insecticide : if it has failed to find one then return 0

BUT i need to allow ability to assess when insecticides have been used previously so may need to pass df_results too

      rot_count <- 1 
      next_insecticide_found <- 0
      candidate <- current_insecticide

      for(temp_int in 1:n_insecticides)
      {
        #search through insecticides and go back to start if reach end
        candidate <- ifelse(candidate==n_insecticides, yes=1, no=candidate+1)

        if (RAF[candidate, 'f','intervention', gen] < rot_criterion)
        {
          next_insecticide_found <- 1 
          current_insecticide <- candidate 
          change_insecticide <- 0

          message(sprintf("generation %d, switch from insecticide %d to %d; frequencies = %f and %f\n",
                          gen, current_insecticide, candidate,
                          RAF[current_insecticide, 'f','intervention', gen], RAF[candidate, 'f','intervention', gen]))
        }

        if (next_insecticide_found==1) break

      } # end of loop checking each insecticide

@@

~ rename rot_count to gens_this_insecticide

@@

~ get an online version up on shinyapps
